### 2023-07-29 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
started to work on contracting discussion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo[inline]{Bryan is here}
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a single vesicle passing through a geometry
that slowly contracts to a region that is only 2~$\mu$m wide, and then
immediately opens back up to a channel that is ten times larger. We
first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, we consider a vesicle with $\alpha =
0.6$ with an initially random initial lipid concentration, one that is
floppy in the front and stiff in the back, and one that is stiff in the
front and floppy in the back. The vesicle with the random initial lipid
distribution phase separates so that the floppy region is in the back
and the stiff region is in the front. The vesicle where the initial
lipid species distribution was fully phase separated and the floppy
region was on the front of the vesicle began to reorient the floppy
region to the back of the vesicle, making it partway after passing
through the contraction. In the case where the initial lipid species
distribution was fully phase separated and the floppy region was on the
back of the vesicle, the floppy region remained on the back of the
vesicle. In all cases, the floppy regions were being oriented to cover
the regions of the vesicle with the highest curvature to minimize the
overall bending energy. Since we can see in
Figure~\ref{fig:RA6leftRightRand} that the regions of high curvature are
located in the back of the vesicle, we expect the overall bending
energies to be lowest for the randomly distributed case and the fully
separated floppy region on the back case. We observe this in
Figure~\ref{fig:RAp6leftRightRandBending} Therefore, in all subsequent
examples, we start with symmetric vesicle whose floppy region is in the
back and its stiff region is in the front.

\begin{figure}[H]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
  $Ca = 0.25$. The lipid distribution is initialized to already be phase
  separated in the top and bottom rows, and the middle row has a random
  initial lipid distribution. The preferred orientation of the lipid
  concentration is to have the stiff region to pass through the
  contraction before the floppy region.}
%  The vesicles are: (a) the initial
%  lipid-species distribution is fully separated on the right side of the
%  vesicle; (b) the initial lipid-species distribution is randomly
%  distributed (not fully separated) on the vesicle membrane; (d) the
%  initial lipid-species distribution is fully separated on the left side
%  of the vesicle. The vesicles with a larger percentage of floppy
%  regions pass through the neck earlier than the vesicles with less
%  percentage of floppy regions. The vesicle either completely or
%  partially reorients itself so that the floppy region is in the back
%  and the stiff region is in the front.}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/bending_leftRightRand.pdf}
  \caption{\label{fig:RAp6leftRightRandBending} The bending energy of a
  multicomponent vesicle that is 50\% stiff with an initial phase
  separation to the left (blue), to the right (red), randomly
  distributed (yellow). The vesicle exits the contraction $x \approx
  15$.} 
\end{figure}

In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha
= 0.5$ and the capillary number is $Ca = 0.25$. We start with a
single-component vesicle and then increase the percentage of the vesicle
membrane that is floppy. By comparing the vesicle location at the time
step just before the vesicle passes through the constriction, we can
immediately see that vesicles with membranes that have larger percentage
of floppy regions reach and pass through the neck earlier. The
dimensionless times that the entire vesicle first passes through the
neck are reported in Table~\ref{tbl:contractingTimes}.

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MC_variableConc.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
  \caption{\label{fig:RA5} \small A vesicle passing through a
  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
  the dimensionless maximum velocity is $Ca = 0.25$. The vesicles are:
  (a) single-component with bending modulus $b=1$; (b) multicomponent
  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
  (d) multicomponent with 35\% floppy region; (e) multicomponent with
  45\% floppy region. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions.}
\end{figure}

\begin{table}[H]
    \centering
    \begin{tabular}{l|c}
       & Time to pass through neck\\
       \hline
       Single-component &  2.32 \\ %2.3173\\
       15\% Multicomponent & 2.30 \\%2.2960\\
       25\% Multicomponent & 2.29 \\%2.2868\\
       35\% Multicomponent & 2.26 \\%2.2637\\
       45\% Multicomponent & 2.24 \\%2.2388\\
       \hline
    \end{tabular}
    \caption{\label{tbl:contractingTimes} The time required for the vesicles to completely pass through the neck located at $x=15$. The vesicles initial center is at $x=5$.}
\end{table}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
    \caption{\small The bending energy for a single-component vesicle (blue) and and a multicomponent vesicle (red)--(green) with $\alpha = 0.5$. As the size of the floppy region increases, the maximum bending energy decreases.}
    \label{fig:bendingAll}
\end{figure}

We conclude this example by considering the different shapes that single-component and multicomponent shapes display. Since we have initialized the lipid species to initially be phase separated, the phase energy is more or less constant for all cases. The tension energy, on the other hand, increases as the vesicle approaches the neck, but its general shape is similar for the five cases considered in Figure~\ref{fig:RA5}. However, the bending energies are show different behaviors for each of the cases (Figure~\ref{fig:bendingAll}). The main difference between the cases is the that multicomponent vesicles with a higher percentage of floppy regions have less bending energy, especially as the vesicle passes through the neck. We also note that the bending energy undergoes several transient increases and decreases. These occur when the tail of the vesicle undergoes transitions from lower energy shapes, such as a `C' or `S' shapes, to high energy shapes, such as 'W' shapes. Figure~\ref{fig:bendingSC_contracting} show these different vesicle shapes for the single-component vesicle and multicomponent vesicle that is 45\% floppy. The shape at several critical points along the bending energy are included, and we can indeed see that transitioning vesicle shape between these different states.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a single vesicle passing through a geometry
that slowly contracts to a region that is only 2~$\mu$m wide, and then
immediately opens back up to a channel that is ten times larger. We
first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, we consider a vesicle with $\alpha =
0.6$ with an initially random initial lipid concentration, one that is
floppy in the front and stiff in the back, and one that is stiff in the
front and floppy in the back. The vesicle with the random initial lipid
distribution quickly phase separates into a two floppy and two stiff
regions. As seen in the stenosis geometry, further phase separation is
delayed until the vesicle is no longer under strong confinement. The
vesicle where the initial lipid species distribution is fully phase
separated with the floppy region on the front of the vesicle begins to
reorient the floppy region to the back of the vesicle. In contrast, the
fully phase separated case with the stiff region at the front maintains
its orientation. In summary, in all three cases, the vesicle is
orienting itself so that the stiff region passes through the
constriction before the floppy region. Therefore, in all subsequent
examples, we start with symmetric vesicle whose floppy region is in the
back and its stiff region is in the front. The vesicle shapes develop
regions with high curvature in the floppy region when they first pass
through the narrowest part of the geometry, but because the strong
confinement is abruptly removed immediately afterwards, these regions of
high curvature are quickly smoothed. 
%Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions
%of high curvature are located in the back of the vesicle, we expect the
%overall bending energies to be lowest for the randomly distributed case
%and the fully separated floppy region on the back case. We observe this
%in Figure~\ref{fig:RAp6leftRightRandBending}.

\begin{figure}[H]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
  $Ca = 0.25$. The lipid distribution is initialized to already be phase
  separated in the top and bottom rows, and the middle row has a random
  initial lipid distribution. The preferred orientation of the lipid
  concentration is to have the stiff region to pass through the
  contraction before the floppy region.}
\end{figure}

%\begin{figure}[H]
%  \centering
%  \includegraphics[width=\columnwidth]{figures/bending_leftRightRand.pdf}
%  \caption{\label{fig:RAp6leftRightRandBending} The bending energy of a
%  multicomponent vesicle that is 50\% stiff with an initial phase
%  separation to the left (blue), to the right (red), randomly
%  distributed (yellow). The vesicle exits the contraction $x \approx
%  15$.} 
%\end{figure}

In addition to the lipid distribution, the percentage of the vesicle
that is floppy plays a role in the vesicle dynamics. Therefore, we
consider a vesicle with reduced area $\alpha = 0.5$ in a contracting
geometry with various sizes of the floppy region. Motivated by the last
experiment, we initialize the lipid distribution so that the front is
stiff and the back is floppy. In each simulation, the capillary number
is $Ca = 0.25$. Figure~\ref{fig:RA5} shows the vesicle shapes as they
pass through the narrow constriction when the percentage of the floppy
region is 0\% (single-component), \%15, \%25, \%35, and \%45. One effect
of the size of the floppy region is that the symmetry of the vesicle
shape is broken at smaller percentages. We also see that stiffer
vesicles have faster migration speeds, but the effect is quite small. In
Table~\ref{tbl:contractingTimes}, we report the time the vesicle first
passes through the neck.
%In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
%$\alpha = 0.5$ and the capillary number is $Ca = 0.25$. We start with a
%single-component vesicle and then increase the percentage of the
%vesicle membrane that is floppy. By comparing the vesicle location at
%the time step just before the vesicle passes through the constriction,
%we can immediately see that vesicles with membranes that have larger
%percentage of floppy regions reach and pass through the neck earlier.
%The dimensionless times that the entire vesicle first passes through
%the neck are reported in Table~\ref{tbl:contractingTimes}.

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MC_variableConc.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
  \caption{\label{fig:RA5} \small A vesicle passing through a
  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
  the Capillary number is $Ca = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=b_{\max}$; (b) multicomponent
  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
  (d) multicomponent with 35\% floppy region; (e) multicomponent with
  45\% floppy region. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions.}
\end{figure}

\begin{table}[H]
  \centering
  \begin{tabular}{l|ccccc}
    \hline
    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% \\ 
    Time  & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:contractingTimes} The time required for the
  vesicles to completely pass through the neck.}
\end{table}
%\begin{table}[H]
%  \centering
%  \begin{tabular}{l|c}
%    Floppy percentage & Time to pass through neck \\
%    \hline
%    0\% &  2.32 \\
%    15\% & 2.30 \\
%    25\% & 2.29 \\
%    35\% & 2.26 \\
%    45\% & 2.24 \\
%%    Single-component &  2.32 \\ %2.3173\\
%%    15\% Multicomponent & 2.30 \\%2.2960\\
%%    25\% Multicomponent & 2.29 \\%2.2868\\
%%    35\% Multicomponent & 2.26 \\%2.2637\\
%%    45\% Multicomponent & 2.24 \\%2.2388\\
%    \hline
%  \end{tabular}
%  \caption{\label{tbl:contractingTimes} The time required for the
%  vesicles to completely pass through the neck.}
%\end{table}

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
  \caption{\label{fig:bendingAll} \small The bending energy for a
  single-component vesicle (blue) and a multicomponent vesicle
  (red)--(green) with $\alpha = 0.5$. As the size of the floppy region
  increases, the maximum bending energy decreases.}
\end{figure}

\todo[inline]{Bryan is here}
We conclude this example by considering the different shapes that
single-component and multicomponent shapes display. Since we have
initialized the lipid species to initially be phase separated, the phase
energy is more or less constant for all cases. The tension energy, on
the other hand, increases as the vesicle approaches the neck, but its
general shape is similar for the five cases considered in
Figure~\ref{fig:RA5}. However, the bending energies are show different
behaviors for each of the cases (Figure~\ref{fig:bendingAll}). The main
difference between the cases is the that multicomponent vesicles with a
higher percentage of floppy regions have less bending energy, especially
as the vesicle passes through the neck. We also note that the bending
energy undergoes several transient increases and decreases. These occur
when the tail of the vesicle undergoes transitions from lower energy
shapes, such as a `C' or `S' shapes, to high energy shapes, such as 'W'
shapes. Figure~\ref{fig:bendingSC_contracting} show these different
vesicle shapes for the single-component vesicle and multicomponent
vesicle that is 45\% floppy. The shape at several critical points along
the bending energy are included, and we can indeed see that
transitioning vesicle shape between these different states.
